---
title: "Remote sensing & reef measurement"
author: "Jerry Moxley"
date: "6/6/2019"
output: html_document
---

```{r echo = F, quiet = T}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(tidyverse)
library(lubridate)
library(plotly)

#data stitch
files = list.files(path = 'data', pattern = "*.csv", 
                    recursive = T, full.names = T)
dat <- sapply(files, read_csv, skip=0, simplify=F) %>% 
  set_names(files) %>% 
  bind_rows(.id = "fname")
#transform
data <- dat %>% 
  mutate(dt = lubridate::ymd(date)) %>% 
  #remove na's from shawna's group
  filter(!is.na(method))
#write_csv(data, "reefMeasurements_ALL.csv")
#daturrrrr furrrrr shawna
```

## Study design

This research focuses on the measurement of reef area from remote sensing products across multiple spatial resolutions.  

Satellite imagery was collected for patch reefs throughout Kaneohe bay between years `r min(year(data$dt), na.rm = T)` - `r max(year(data$dt), na.rm = T)` from multiple platforms & providers (e.g., WorldView 1/2, GeoEye-1, Quickbird, Ikonos, PLanetScope, Rapid Eye, Sentinel-2, and finally.... yes.. Landsat 8).  

In May-June 2019, three field crews collected in situ measurements of these reefs to compare the accuracy of direct field estimates of reef area and perimeter to estimates derived from remote sensing.  

This analysis compares measurement variability across data types (i.e., in situ & remote sensing). 

##Analysis
```{r echo = F}
#look at the data
df <- data %>% 
  select(area_m2, perimeter_m, 
         reef_no, replicate, res = imagery_resolution_m, 
         method, platform, imagery_type, provider, observer, 
         dt) %>% 
  gather(var, val, -reef_no, -replicate, -res, -method, -platform, 
         -imagery_type, -provider, -observer, -dt)


p <- df %>% 
  ggplot() + 
  geom_histogram(aes(x = val, fill = observer)) + 
  facet_grid(reef_no~var, scales = "free") +
  theme_bw()
ggplotly(p)

#outliers exist, remove beyond 2SD
df <- df %>%
  group_by(reef_no, var) %>%
  filter(!(abs(val - median(val)) > 2*sd(val))) 
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
